%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Þórður Hermannsson -- Résumé} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Date of Birth} \> 24$^{th}$ September 1987\\ % Date of birth 
{\bf Nationality} \> Icelandic % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +(354) 6906649 \\ % Mobile phone
{\bf Email} \> \href{mailto:doddi@kott.is}{doddi@kott.is} \\ % Email address
{\bf Github} \> \href{https://github.com/naglalakk}{github.com/naglalakk} \\ % Github
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

My name is Þórður Hermannsson. I work as a freelance programmer for various different clients building solutions of all shapes and sizes. Currently my main focus is in web development. My main goal is building sustainable and reliable products for my clients and currently I'm investing a lot of my technology stack in purely functional programming languages such as Haskell and Purescript. 

%----------------------------------------------------------------------------------------
%	PROJECT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\job
{July 2018-}{Present}
{Sena/Sena Live, Iceland}
{https://www.sena.is, https://www.senalive.is}
{Main Developer}
{Sena is one of the biggest companies working in the entertainment industry in Iceland. I currently maintain both of their sites which run on the Wordpress CMS.\\
\rule{0mm}{5mm}\textbf{Tags:} Wordpress, CMS, Apache\\
\rule{0mm}{5mm}\textbf{Website: }https://sena.is, https://senalive.is}

\job
{July 2018-}{Present}
{Iceland Airwaves, Iceland}
{https://icelandairwaves.is}
{Main Developer}
{Iceland Airwaves is a widely known music festival that takes place every year in Reykjavik, Iceland. I maintain their site which runs on the Wordpress CMS. Additionally I manage syncing their data for the schedule each year so that it's up to date on the site and in the Iceland Airwaves app, available for both Android and iOS. The API serving the data for the schedule runs seperately and is written in Haskell.\\
\rule{0mm}{5mm}\textbf{Tags:} Wordpress, CMS, Apache, Haskell\\
\rule{0mm}{5mm}\textbf{Website:} https://icelandairwaves.is
}

\job
{2018}{}
{Our Atlantis}
{https://djflugveloggeimskip.com}
{Game Developer}
{In 2017 me and artist Steinunn Harðardóttir made a video game based on her art and music. The game was developed in Unity over the period of 6 months. The video game is based on collecting loops and each loops plays a short clip from Steinunn's song. This way the player travels through the song depending on his actions within the game. The game has been showcased on various game festivals in Reykjavik, Iceland.\\
\rule{0mm}{5mm}\textbf{Tags:} Unity, Game development\\
\rule{0mm}{5mm}\textbf{Website:} https://djflugveloggeimskip.com
}

\newpage

\job
{Sep 2016-}{2018}
{Codecov, Netherlands/Iceland}
{https://www.codecov.io}
{Software Developer}
{Codecov is a company specialized in making products for analysing and displaying code coverage data.\\
At Codecov I worked on increasing performance in places where speed is critical.\\
\rule{0mm}{5mm}\textbf{Tags:} Python, C.\\
\rule{0mm}{5mm}\textbf{Website:} https://codecov.io 
}

\job
{Jan 2014-}{Present}
{CompetitionFeed, Reykjavik, Iceland}
{http://www.competitionfeed.com}
{System Administrator, Software Developer}
{CompetitionFeed is a feed reader made for competition authorities around the world. \\
\rule{0mm}{5mm}\textbf{Tags:} Ruby, Javascript, Rails, Redis, Memcached, Elasticsearch, Postgresql\\
\rule{0mm}{5mm}\textbf{Website:} https://competitionfeed.com
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{Sept 2015-}{Sept 2016}
{Tempo, Reykjavik, Iceland}
{http://www.tempo.io}
{DevOps, Software Developer}
{Tempo is a company that makes time tracking tools intigrated into agile solutions such as Atlassian Jira.
While working there I was included in multiple teams. My work included DevOps, web programming, system administration and programming for multiple different platforms including mobile devices.\\
\rule{0mm}{5mm}\textbf{Tags:} Python, Javascript, Shell, iOS, Android, Docker, Postgresql\\
\rule{0mm}{5mm}\textbf{Website:} https://tempo.io
}

%------------------------------------------------

\job
{Jan 2015-}{Sept 2016}
{DV EHF, Reykjavik, Iceland}
{http://www.dv.is}
{System Administrator, Software Developer}
{DV is one of the biggest news agency in Iceland. My job was to maintain their news website dv.is as well as handling all DevOps related tasks.\\
\rule{0mm}{5mm}\textbf{Tags:} Python, Django, Redis, Memcached, Elasticsearch, Postgresql\\
\rule{0mm}{5mm}\textbf{Website:} https://dv.is
}

%------------------------------------------------

\job
{May 2014-}{Jan 2015}
{Integral Turing, Reykjavik, Iceland}
{http://www.turing.is}
{Software Developer}
{Integral Turing is a company that makes web solutions. My work at Integral Turing was to help build their peer-to-peer car rental platform.
The solution is programmed in Python with the Django Web Framework.\\
\rule{0mm}{5mm}\textbf{Tags:} Javascript, Python/Django, Shell, Postgresql\\
\rule{0mm}{5mm}\textbf{Website:} http://turing.is
}

%------------------------------------------------

\job
{Jan 2013-}{May 2014}
{Fancy Pants Global, Reykjavik, Iceland}
{https://www.linkedin.com/company/fancy-pants-global/}
{Software Developer}
{Worked on Mobile Appplication development as well as developing web applications in C\# ASP.NET. \\
\rule{0mm}{5mm}\textbf{Tags:} Cocoa, iOS, ASP.NET, C\#, Shell, Postgresql}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2011-2014} \> Computer Science - \href{http://www.ru.is}{The University of Reykjavik, Iceland} \\[5pt]
\bf{2007-2010} \> Composition - \href{http://www.lhi.is}{Iceland Art Academy, Iceland} \\[5pt]
}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Programming Languages}
{
Haskell\\
Purescript\\
\textit{Python}\\
\textit{C}\\
C\#\\
C++\\
\textit{Ruby}\\
\textit{Javascript}
}

%------------------------------------------------

\skillgroup{Web Development}
{
HTML, \textit{HTML5, CSS3/SASS, JavaScript/ES6CoffeeScript/jQuery}\\
Halogen       - Language: Purescript, Tag: Web Framework\\
Servant       - Language: Haskell, Tag: API Framework\\
Ruby on Rails - Language: Ruby, Tag: Web Framework\\
\textit{Django}        - Language: Pyton, Tag: Web Framework \\
\textit{Apache/Nginx Web Servers}
}

%------------------------------------------------

\skillgroup{Miscellaneous}
{
\textit{Unity} - Game Engine\\
\textit{Docker} - Containerization \\
\textit{Elasticsearch} - Search engine\\
\textit{Redis} - Cache\\
\textit{Memcached} - Cache\\
\textit{Postgresql} - Relational Database Management System\\
\textit{MySQL Server}
}

\end{document}
